The Morality of Arbitrage

### 2017-04-23 Draft/draft2.tex
Updating draft2.

\noindent  \section{Introduction}\label{introduction}

\begin{quote}
{[}T{]}he shipper who earns his living from using otherwise empty or
half-filled journeys of tramp-steamers, or the estate agent whose whole
knowledge is almost exclusively one of temporary opportunities, or the
\emph{arbitrageur} who gains from local differences of commodity prices,
are all performing eminently useful functions based on special knowledge
of circumstances of the fleeting moment not known to others. -- F.A.
Hayek
\end{quote}

>>>>

\noindent  \begin{quote}
{[}T{]}he shipper who earns his living from using otherwise empty or
half-filled journeys of tramp-steamers, or the estate agent whose whole
knowledge is almost exclusively one of temporary opportunities, or the
\emph{arbitrageur} who gains from local differences of commodity prices,
are all performing eminently useful functions based on special knowledge
of circumstances of the fleeting moment not known to others. -- F.A.
Hayek
\end{quote}

\section{Introduction}\label{introduction}
